High Contrast Coronagraphy

### 2024-09-18 src/tex/ms.tex
removed errant comma

%
Other methods try to linearize phase diversity in either imaging mode or coronagraphy mode because linear methods allow for short computational times.
%
There is the Linearized focal plane technique \citep[LIFT; ][]{meimon2010lift}, or the linearized Analytical Phase Diversity \citep[LAPD; ][]{vievard2020cophasing}.
%
Certain coronagraphs also use algorithms that are specific to their behavior such as QACITS \citep{huby2017sky} for the \ac{ovc}.
%
QACITS is a tip/tilt centering algorithm to keep the star on top of the center of the \ac{ovc} mask resulting in a pointing stability of 2.4 mas over several hours. 
%
Most phase diversity methods aim to control only the low-order Zernike modes.
%
However, most coronagraphic dark holes are dug at medium spatial frequencies.
%
Linearized Dark Field Control \citep[LDFC;][]{miller2017spatial} is a method that extends beyond just a few low-order modes.
%
This method has been shown on-sky with the vAPP coronagraph and is being investigated to work with arbitrary coronagraphs \citep{,miller2019spatial,ahn2023combining}.
%
The push for linear methods was due to computational complexity of the non-linear reconstruction algorithms.
%
Recent advances in machine learning have also made it possible to run deep neural networks with short inference times at real time rates.
%
These, often data-driven, methods can be used to solve the non-linear phase retrieval methods.
%
Variations on the neural network architecture allow for either normal imaging \citep{orban2021focal, zhang2021phasegan}, post-coronagraphic imaging \citep{quesnel2022deep} or used within an iterative scheme like `fast and furious' \citep{bottom2023sequential}.

>>>>

%
Other methods try to linearize phase diversity in either imaging mode or coronagraphy mode because linear methods allow for short computational times.
%
There is the Linearized focal plane technique \citep[LIFT; ][]{meimon2010lift}, or the linearized Analytical Phase Diversity \citep[LAPD; ][]{vievard2020cophasing}.
%
Certain coronagraphs also use algorithms that are specific to their behavior such as QACITS \citep{huby2017sky} for the \ac{ovc}.
%
QACITS is a tip/tilt centering algorithm to keep the star on top of the center of the \ac{ovc} mask resulting in a pointing stability of 2.4 mas over several hours. 
%
Most phase diversity methods aim to control only the low-order Zernike modes.
%
However, most coronagraphic dark holes are dug at medium spatial frequencies.
%
Linearized Dark Field Control \citep[LDFC;][]{miller2017spatial} is a method that extends beyond just a few low-order modes.
%
This method has been shown on-sky with the vAPP coronagraph and is being investigated to work with arbitrary coronagraphs \citep{miller2019spatial,ahn2023combining}.
%
The push for linear methods was due to computational complexity of the non-linear reconstruction algorithms.
%
Recent advances in machine learning have also made it possible to run deep neural networks with short inference times at real time rates.
%
These, often data-driven, methods can be used to solve the non-linear phase retrieval methods.
%
Variations on the neural network architecture allow for either normal imaging \citep{orban2021focal, zhang2021phasegan}, post-coronagraphic imaging \citep{quesnel2022deep} or used within an iterative scheme like `fast and furious' \citep{bottom2023sequential}.
